### 2020-03-16 writeup/setup.tex
wip

A natural setting is when the covariance matrices $X_i^{\top} X_i$ are different, i.e. having different spectrum.
This is also known as covariate shift in the literature.
Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.

@@

When the models are the same for all tasks, we use a simplified objective as follows.
\begin{align}
	\label{eq_mtl_basic}
	f(w) = \sum_{i=1}^k \norm{X_i w - Y_i}^2.
\end{align}
%{\bf The distributed learning problem.}
%    \begin{align}
%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
%   \end{align}

Equation \eqref{eq_mtl} is a slightly more complicated parametrization of equation \eqref{eq_mtl_basic}, in that each $A_i$ can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.

@@

The most general version is when the covariates are different between different tasks and the single-task models are also different.
Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.

We remove the assumption that the models are the same.
The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^d$.
\begin{align}
	y_i = X_i \beta_i + \varepsilon_i.
\end{align}

@@

We will designate the $k$-th task as the target.
Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task.
Concretely, we focus on two objectives.
\begin{itemize}
	\item Estimation error for the target model $\beta_t$: we consider their distance
		\[ \exarg{\varepsilon}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
	\item Test error for the target task:
		\[ \exarg{x \sim \Sigma_k}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}. \]
\end{itemize}
%\todo{may also consider test error}
%Several relevant directions on this setting.
%\begin{itemize}
%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
%\end{itemize}

>>>>

A natural setting is when the covariance matrices $\frac{1}{n_i}\cdot X_i^{\top} X_i$ are different, i.e. having different spectrum or singular vectors.
This is also known as covariate shift in the literature.
\todo{Our hypothesis is that the covariate shift can slow down the convergence of learning the true $\theta$ as a function of the number of data points.}

@@

When the models are the same for all tasks, we use a simplified objective as follows.
\begin{align}
	\label{eq_mtl_basic}
	f(w) = \sum_{i=1}^k \norm{X_i w - Y_i}^2.
\end{align}
%{\bf The distributed learning problem.}
%    \begin{align}
%     f(w) = \sum_{i=1}^k \normFro{X_i w - Y_i}^2. \label{eq_dist}
%   \end{align}
Equation \eqref{eq_mtl_basic} is simplified from Equation \eqref{eq_mtl} by setting $A_i$ to be 1 for all tasks. %can select a model from the subspace of $B$ to fit $(X_i, Y_i)$.

@@

In addition to covariate shift, in general the single-task models can also be different across different tasks.
\todo{Here the hypothesis is that the optimal $B$ is captured by a low-rank approximation of the single-task models.}
%We remove the assumption that the models are the same.
The $i$-th task data can be viewed as generated by a separate model $\beta_i\in\real^p$.
\begin{align}
	Y_i = X_i \beta_i + \varepsilon_i.
\end{align}

@@

We will designate the $k$-th task as the target.
Our goal is to come up with an estimator $\hat{\beta}$ to provide accurate predictions for the target task, provided with the other auxiliary task data.
Concretely, we focus on two objectives.
\begin{itemize}
	\item Estimation error for the target model $\beta_t$: we consider their distance
		\[ \exarg{\varepsilon_i, \forall 1\le i\le k}{\bignorm{\hat{\beta} - \beta_t}^2}. \]
	\item Test error for the target task:
		\[ \exarg{x \sim \Sigma_k}{\exarg{{\varepsilon_i, \forall 1\le i\le k}}{(x^{\top}\hat{\beta} - x^{\top}\beta_t)^2}}. \]
\end{itemize}
%\todo{may also consider test error}
%Several relevant directions on this setting.
%\begin{itemize}
%  \item {\bf Low-rank space of $\set{\theta_i}_{i=1}^k$.} We may assume that the task models themselves form a low-rank space. This imposes that the tasks should be related to each other in some way.
%  \item {\bf PCA-based averaging for distributed regression.} This also leads to a natural heuristic for the distributed learning problem.
%    After receiving $\hat{\theta_i}$, for $i = 1, 2,\dots, k$, we can apply PCA to find a low-rank space of the estimates.
%  \item {\bf The hypothesis testing view.} A practical question that often arises in MTL is, if we can access a new task data (say $k+1$-th), should we add the task to the existing set of tasks or not?
%    One hypothesis is to find the projecion of $\hat{\theta}_{k+1}$ to the low-rank space of the estimates.
%  \item {\bf MTL and matrix factorization.} Could we use the results from MF to solve MTL? Does the landscape of MTL connect to MF?
%\end{itemize}
